---
title       : 1974 Road Testing
subtitle    : Motor Trend Magazine 
author      : S101 for the Coursera Data Scientist Spesialisation, Data Products module
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : Xcode  #default # change the presentation of rcode Xcode also has r code without colour blocks or outlines :)
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : standalone # {selfcontained, draft}
knit        : slidify::knit2slides

 # good websites:
 # https://highlightjs.org/static/demo/
 # https://www.uvm.edu/rsenr/vtcfwru/R/fledglings/14_Slideshows.html
 # https://code.google.com/p/slidifylibraries/source/browse/inst/libraries/frameworks/io2012/css/slidify.css?r=f9b80e4b5ae02a0a8dd8688e4b6d1cf1852281b6
 # http://zevross.com/blog/2014/11/19/creating-elegant-html-presentations-that-feature-r-code/
---
<!-- Limit image width and height -->
  <style type='text/css'>
  img {
    max-height: 460px;
    max-width: 664px;
  }
</style>
  

## Goal

When shopping for a new car, what factors affect the rate of fuel consumption? Does the transmission/number of cylinders affect the miles per gallon (mpg)? 

* I've developled a simple shiny app that lets us visulise this and see if there are any patterns across a variety of makes-models.

### From a project point of view...
This presentation was created as part of the peer assessment for the coursera developing data products class. The assignment is designed to build knowledge and understanding of:  
* The shiny package to build a data application
* use of R-Presentation or slidify to create a presentation (ie this one about the app) 

--- &twocol

## The Data 

Extracted from the 1974 Motor Trend US magazine 
Tested 32 make-models of car (1973-74 models)
Data comprises fuel consumption (Miles/(US) gallon) and 10 aspects of automobile design and performance:  

***=left
1. Number of cylinders
2. Displacement (cu.in.)
3. Gross horsepower
4. Rear axle ratio
5. Weight (lb/1000)

***=right
6. 1/4 mile time
7. V/S
8. Transmission
9. Number of forward gears
10. Number of carburetors

***=fullwidth
Datasource: Henderson and Velleman (1981), Building multiple regression models interactively. Biometrics, 37, 391-411.

---

## The App
Explore the relationship between the 10 car design and performance variables and the car's fuel consumption in miles per gallon (mpg) via a point plot (using the ggplot2 libray) 

# To use this app
* Choice of descriptor variables via the 'X' dropdown, default: weight (lb/1000)
* The Y axis (responce variable) is limited to miles per gallon (mpg) 
* Use the 'Grouping' dropdown to decide whether to examine data groupings using colour, default: transmission type
* View one or multiple plots by cylinder-, gear-, carburetor- number, or transmission type using the 'Facits' Row and Column dropdowns
* View distribution of data points via the 'Data distribution' check box
* Option provided to fit a simple y~x model to the selected data, when grouping/facets selected one model per data subset. Visulised through predicted fits with 95% confidence intervals. Five methods to choose from: linear, generalised linear model,generalised additive, local polynomial, or robust linear (iterated re-weighted least squares)

--- &twocol

## Underlying Code
When, for example, x axis = 'weight', y axis = 'mpg', grouping = 'transmission', the simple model fit box is checked and the 'pick modelling method' is set to lm the following ggplot is produced with two liner a linear models fitted, one of manual transmissions and one for automatics.  

*** =left
 
```{r,echo=FALSE, message=FALSE,warning=FALSE}
library(ggplot2)
mtcars$Transmission<-factor(mtcars$am,labels= c('automatic', 'manual'))
ggplot(mtcars, aes(x=wt, y=mpg,colour=Transmission)) + 
  geom_point() + 
  xlab("Weight") + 
  scale_colour_brewer(palette="Set1") + 
  geom_smooth(method="lm")
```

*** =right

```{r,eval=FALSE,echo=TRUE}
ggplot(mtcars, aes(x=wt, y=mpg,
                   colour=Transmission)) + 
  geom_point() + 
  xlab("Weight") + 
  scale_colour_brewer(palette="Set1") + 
  geom_smooth(method="lm")
```






